# [Facets (ggplot2)](http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/)

## Problem
You want to do split up your data by one or more variables and plot the subsets of data together.
## Solution
We will use the tips dataset from the reshape2 package.
```{r}
library(ggplot2)
library(reshape2)
head(tips,3)
```
```{r}
sp0 <- ggplot(data=tips,
             aes(x=total_bill, y=tip/total_bill)) + geom_point(shape=1)
#The data can be split up by one or two variables that vary on the #horizontal and/or vertical direction.
#This is done by giving a formula to facet_grid(), of the form #vertical ~ horizontal.
sp1<-sp0 + facet_grid(sex ~ day)
#Instead of faceting with a variable in the horizontal or vertical #direction, facets can be placed next to each other, wrapping with #a certain number of columns or rows. The label for each plot will #be at the top of the plot.
# Divide by day, going horizontally and wrapping with 2 columns
sp2<-sp0+facet_wrap( ~ day, ncol=2)

sp0
sp1
sp2
```
## Modifying facet label appearance
```{r}
sp1 +theme(strip.text.x = element_text(size=8, angle=35),
          strip.text.y = element_text(size=12, face="bold"),
          strip.background = element_rect(colour="grey",fill="pink"))
```
## Free scales
Normally, the axis scales on each graph are fixed, which means that they have the same size and range. They can be made independent, by setting scales to free, free_x, or free_y.
```{r}
# A histogram of bill sizes
hp <- ggplot(data=tips, 
             aes(x=total_bill)) + geom_histogram(binwidth=2,colour="white")

# Histogram of total_bill, divided by sex and smoker
hp + facet_grid(sex ~ smoker)

# Same as above, with scales="free_y"
hp + facet_grid(sex ~ smoker, scales="free_y")

# With panels that have the same scaling, but different range (and therefore different physical sizes)
hp + facet_grid(sex ~ smoker, scales="free", space="free")


```

