## Frequency Polygons

+ They are similar to histograms, but they draw a curve connecting the counts in a histogram.  
+ It allows us to see the shape and the peaks of our distribution in more detail.
+ Note that the shape of the frequency polygon depends on how our *bins* are set up - the height of the lines are the same as the bars in individual histograms, but the lines are easier to make a comparison with since they are on the same axis.
+ Note that *sum(..count..)* will sum across color, so the percentages displayed are percentages of total users. To plot percentages within each group, you can try *y = ..density...*
```{r}
getwd()
setwd("/Users/henry/Desktop/Data Science/ud651_data_analysis_with_R/lesson3")

pf<-read.csv('pseudo_facebook.tsv',sep='\t')
library(gridExtra)
library(ggplot2)
names(pf)
#histogram
p1<-ggplot(data=subset(pf,!is.na(gender)),
           aes(x=friend_count))+
  geom_histogram(binwidth=10)
#frequency polygon
p2<-ggplot(data = subset(pf,!is.na(gender)),
           aes(x=friend_count))+
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Number of users with that friend count')



#show the proportions instead of raw counts, so we will pass in y
#percentages of total users
p3<-ggplot(data = subset(pf,!is.na(gender)),
           aes(x=friend_count,y=..count../sum(..count..)))+
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count-binwidth=10') + 
  ylab('Proportion of users with that friend count')


#plot percentages within each group
p4<-ggplot(data = subset(pf,!is.na(gender)),
           aes(x=friend_count,y=..density..))+
  geom_freqpoly(aes(color = gender), binwidth=50) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count-binwidth=50') + 
  ylab('Proportion of users with that friend count')


grid.arrange(p1,p2,p3,p4,ncol=1)
```
```{r}
names(pf)
by(pf$www_likes,pf$gender,summary)
by(pf$www_likes,pf$gender,sum)


ggplot(data=subset(pf,!is.na(gender)),
       aes(x=www_likes))+
  geom_freqpoly(aes(color=gender),binwidth=1)+
  scale_x_log10()
```

