# [Cartesian coordinates](http://docs.ggplot2.org/current/coord_cartesian.html)
## Usage
coord_cartesian(xlim = NULL, ylim = NULL, expand = TRUE)

## Arguments

 + xlim, ylim  
Limits for the x and y axes.
 + expand  
If TRUE, the default, adds a small expansion factor to the limits to ensure that data and axes don't overlap.   
If FALSE, limits are taken exactly from the data or xlim/ylim.

## Description  
The Cartesian coordinate system is the most familiar, and common, type of coordinate system. Setting limits on the coordinate system will zoom the plot (like you're looking at it with a magnifying glass), and will not change the underlying data like setting limits on a scale will.

## Examples
```{r}
data("mtcars")
library(ggplot2)
library(gridExtra)
names(mtcars)
str(mtcars)
```
```{r}
# There are two ways of zooming the plot display: with scales or
# with coordinate systems.  They work in two rather different ways.


p0<-ggplot(data=mtcars,aes(disp,wt))+
  geom_point(color='black')+
  geom_smooth()+
  scale_x_continuous(breaks=seq(0,500,50))
# Setting the limits on a scale converts all values outside the range to NA.
p1<-p0+scale_x_continuous(limits = c(325, 500))

# Setting the limits on the coordinate system performs a visual zoom.
# The data is unchanged, and we just view a small portion of the original
# plot. Note how smooth continues past the points visible on this plot.
p2<-p0+coord_cartesian(xlim = c(325, 500))
# Simiarly, we can use expand = FALSE to turn off expansion with the
# default limits
p3<-p0+coord_cartesian(xlim = c(325, 500),expand = FALSE)


grid.arrange(p0,p1,p2,p3,ncol=2)
```


