---
title: "data_types"
author: "Wenhan Ji"
date: "2017??4??3??"
output: html_document
---

[Tutorial](http://www.statmethods.net/input/datatypes.html)

#Data Types
R has a wide variety of data types including scalars, vectors (numerical, character, logical), matrices, data frames, and lists.


#Vectors

###create vectors
```{r}
a<-c(3,1.1,2.2,-3) #numeric vector
b<-c("one","two","three")#character vector
c<-c(TRUE,FALSE,TRUE,FALSE)#logical vector
a
b 
c
```

###Refer to elements of a vector using subscripts
```{r}
c(2,4)
a[c(2,4)]# 2nd and 4th elements of vector
a[1:3] #1st to 3rd elemets of a vector
```

#Matrices
All columns in a matrix must have the same mode(numeric, character, etc.) and the same length. The general format is

mymatrix <- matrix(vector, nrow=r, ncol=c, byrow=FALSE, 
  	dimnames=list(char_vector_rownames, char_vector_colnames))

byrow=TRUE indicates that the matrix should be filled by rows. byrow=FALSE indicates that the matrix should be filled by columns (the default). dimnames provides optional labels for the columns and rows.
```{r}
# generates 5 x 4 numeric matrix #fill by columns
y<-matrix(1:20, nrow=2,ncol=10,byrow=TRUE)
y
# another example
cells <- c(1,26,24,68)
rnames <- c("R1", "R2")
cnames <- c("C1", "C2") 
mymatrix <- matrix(cells, nrow=2, ncol=2, byrow=TRUE,
  dimnames=list(rnames, cnames))

mymatrix

rownames(mymatrix)
colnames(mymatrix)
```

#Data Frames
A data frame is more general than a matrix, in that different columns can have different modes (numeric, character, factor, etc.). 

```{r}
d<-c(1,2,3,4)
e<-c(TRUE,TRUE,TRUE,FALSE)
f<-c("blue","green","grey",NA)

mydf<-data.frame(d,e,f)
names(mydf)<-c("ID","Passes","Color") #variable names
row.names(mydf)<-c("a","b","c","d") #instance names

mydf[1:2] #columns 1,2 of df
mydf[c("ID","Color")]#ID and Color column
mydf$ID      #variable ID in the dataframe

mydf[1:2,]   #row 1:2, all col

mydf
```

#Lists
An ordered collection of objects (components). A list allows you to gather a variety of (possibly unrelated) objects under one name.

```{r}
# example of a list with 4 components - 
# a string, a numeric vector, a dataframe, and a scaler 
a<-c(1,2,3,4)
f<-c("blue","green","grey",NA)
mydf<-data.frame(a,f)

list1 <- list(name="Fred", mynumbers=a, myframe=mydf, age=18)
list1

list1[1]
list1[[1]]
```
```{r}
# example of a list containing two lists using c
list2<-list(name="Henry", age=21)
v<-c(list1,list2)
v[1:7]
```
```{r}
#Identify elements of a list using the [[]] convention
list1[[2]] # 2nd component of the list
list1[["mynumbers"]] # component named mynumbers in list
```

#Factors
Tell R that a variable is nominal by making it a factor.
The factor stores the nominal values as a vector of integers in the range [ 1... k ] (where k is the number of unique values in the nominal variable), and an internal vector of character strings (the original values) mapped to these integers.
```{r}
# variable gender with 20 "male" entries and 
# 30 "female" entries 
c(rep("repeat", 3))
gender <- c(rep("male",2), rep("female", 3),"Unknown") 
gender <- factor(gender) 
# stores gender as 20 1s and 30 2s and associates
# 1=female, 2=male internally (alphabetically)
# R now treats gender as a nominal variable 
str(gender)

#summary(gender)

table(gender)
```
#Ordered factor
An ordered factor is used to represent an ordinal variable.
```{r}
# recodes rating to 1,3,5 and associates
# 5=large, 3=medium, 1=small internally
# R now treats rating as ordinal
rating<-c(rep("large",3),rep("small",1),rep("medium",3))
table(rating)



#map small to 1, medium to 3, large to 5
rating<-ordered(rating,levels=c("small","medium","large"))
                
table(rating)
levels(rating)

str(rating)


```

R will treat factors as nominal variables and ordered factors as ordinal variables in statistical proceedures and graphical analyses. 
You can use options in the factor( ) and ordered( ) functions to control the mapping of integers to strings (overiding the alphabetical ordering). 

#Useful Functions
```{r}
length(rating) # number of elements or components
str(rating)    # structure of an object 
class(rating)  # class or type of an object
names(rating)

current_obj=ls()# list current objects
str(current_obj)

```


```{r}
rm(list=ls()) # delete all object-global environment
ls()
```

