---
title: "3.2ordered_factor_variables.Rmd"
author: "Wenhan Ji"
date: "2017Äê4ÔÂ3ÈÕ"
output: html_document
---

[tutorial link](http://stats.idre.ucla.edu/r/modules/factor-variables/)


#1. Creating factor variables
Factor variables are categorical variables that can be either numeric or string variables. There are a number of advantages to converting categorical variables to factor variables. Perhaps the most important advantage is that they can be used in statistical modeling where they will be implemented correctly, i.e., they will then be assigned the correct number of degrees of freedom.

+ The only required argument is a vector of values which can be either string or numeric.
+ The levels argument, which determines the categories of the factor variable, and the default is the sorted list of all the distinct values of the data vector. 
+ The labels argument, which is a vector of values that will be the labels of the categories in the levels argument. 

The problem is that the levels are ordered according to the alphabetical order of the categories of ses. Thus, ¡°high¡± is the lowest level of ses.f.bad.order, ¡°middle¡± is the middle level and ¡°low¡± is the highest level. In order to fix the ordering we need to use the levels argument to indicate the correct ordering of the categories. Let¡¯s create a new factor variable called ses.f with the correct order of categories.
```{r}
#generate numeric vector
state<-sample(0:1 ,20,replace=TRUE)
state
is.factor(state)
is.numeric(state)

#generate factor variable
state.f<-factor(state,labels=c("private","public"))
levels(state.f)
table(state.f)
#generate a character vector
status.rank <- c("low", "middle", "low", "low", "low", "low", "middle","low", "middle","middle", "middle", "middle", "middle",  "high", "high", "low", "middle","middle", "low", "high")
is.character((status.rank))
#use the levels argument to indicate the correct ordering of the categories
status.rank.f<-factor(status.rank,levels=c("low","middle","high"))
status.rank.f
levels(status.rank.f)

```

#2. Creating ordered factor variables

```{r}
#method1
status.rank.o<-ordered(status.rank,levels=c("low","middle","high"))
#method2
status.rank.fo<-factor(status.rank,levels=c("low","middle","high"),ordered=TRUE)
status.rank.o
status.rank.fo
```
#3. Adding and dropping levels in factor variables
```{r}
#add level
length(status.rank.f)
status.rank.f<-factor(status.rank.f,levels=c(levels(status.rank.f),"very.high"))
status.rank.f[21] <- "very.high"
status.rank.f
```
```{r}
status.rank.f<-status.rank.f[status.rank.f!="very.high"]
status.rank.f
#drop the none exist level
status.rank.f<-factor(status.rank.f)
status.rank.f
```
```{r}
table(state.f)
table(status.rank.f)
table(state.f,status.rank.f)
```

