Lesson 4
========================================================
http://docs.ggplot2.org/current/

http://bbs.ceb-institute.org/wp-content/uploads/2011/09/handout_ggplot2.pdf
```{r}
getwd()
library(ggplot2)
pf<-read.csv('pseudo_facebook.tsv',sep='\t')
```
### Scatterplots and Perceived Audience Size
```{r }
summary(pf$age)
```

```{r}
#plus operator add a new layer to our figure
ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_point(shape=1,size=1)+
  xlim(13,90)
```
### Overplotting
Overplot makes it difficult to tell how many points are in each region. So we can set the transpancy of points using *alpha* parameter.

```{r Overplotting}

#It's going to take 20 points to be equivalent of one of these black dots. 
library(gridExtra)
p1<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_point(shape=1,size=1,alpha=1/20)+
  xlim(13,90)

#age is a continuous variable, but I only have integer variables, so are are seeing the perfectly lined up columns, which isn't a true reflection of age.
#Using jitter, we can add some noise to each age so we can get a clearer picture about the relationship between age and friend count.
p2<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_jitter(shape=1,size=1,alpha=1/20)+
  xlim(13,90)

grid.arrange(p1,p2,ncol=1)
```

### Coord_trans()
Look up the documentation for coord_trans() by running this line of code  *?coord_trans* or visit   http://docs.ggplot2.org/current/coord_trans.html.

```{r Coord_trans()}
p3<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_jitter(shape=1,size=1,alpha=1/20)+
  xlim(13,90)+
  coord_trans(x="sqrt")
p3
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

