Lesson 4
========================================================
http://docs.ggplot2.org/current/

http://bbs.ceb-institute.org/wp-content/uploads/2011/09/handout_ggplot2.pdf
```{r}
getwd()
library(ggplot2)
pf<-read.csv('pseudo_facebook.tsv',sep='\t')
```
### Scatterplots and Perceived Audience Size
```{r }
summary(pf$age)
```

```{r}
#plus operator add a new layer to our figure
ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_point(shape=1,size=1)+
  xlim(13,90)
```
### Overplotting
Overplot makes it difficult to tell how many points are in each region. So we can set the transpancy of points using *alpha* parameter.

```{r Overplotting}

#It's going to take 20 points to be equivalent of one of these black dots. 
library(gridExtra)
p1<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_point(shape=1,size=1,alpha=1/20)+
  xlim(13,90)

#age is a continuous variable, but I only have integer variables, so are are seeing the perfectly lined up columns, which isn't a true reflection of age.
#Using jitter, we can add some noise to each age so we can get a clearer picture about the relationship between age and friend count.
p2<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_jitter(shape=1,size=1,alpha=1/20)+
  xlim(13,90)

grid.arrange(p1,p2,ncol=1)
```

### Coord_trans()
Look up the documentation for coord_trans() by running this line of code  *?coord_trans* or visit   http://docs.ggplot2.org/current/coord_trans.html.

+ I am visualize every point in the dataset. In general, it's difficult to judge important quantities from such a display.

```{r Coord_trans()}
p3<-ggplot(data=pf,
       aes(x=age,y=friend_count))+
  geom_jitter(shape=1,size=1,alpha=1/20,
              position=position_jitter(height=0))+
  xlim(13,90)+
  coord_trans(x="sqrt")
p3
```

