https://blog.rstudio.org/2014/01/17/introducing-dplyr/

http://rstudio-pubs-static.s3.amazonaws.com/11068_8bc42d6df61341b2bed45e9a9a3bf9f4.html
### Conditional Means
Sometimes you want to understand how the mean or median of a variable varies with another variable. It can be helpful to summarize the relationship between two variable in other ways rather than just plotting every single point.

+ We can ask how does the average friend count vary over age.
+ dplyr lets up split up a dataframe and apply a function to some parts of the data
+ common functions: filter,groupby,mutate,arrange
```{r Conditional Means}

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***