https://blog.rstudio.org/2014/01/17/introducing-dplyr/

http://rstudio-pubs-static.s3.amazonaws.com/11068_8bc42d6df61341b2bed45e9a9a3bf9f4.html
### Conditional Means
Sometimes you want to understand how the mean or median of a variable varies with another variable. It can be helpful to summarize the relationship between two variable in other ways rather than just plotting every single point.

+ For each age, it gives us the mean and median for income.
+ We can ask how does the average friend count vary over age.
+ dplyr lets up split up a dataframe and apply a function to some parts of the data
+ common functions: filter,groupby,mutate,arrange
```{r Conditional Means}
library(dplyr)
library(ggplot2)
pf<-read.csv('pseudo_facebook.tsv',sep='\t')
##group my dataframe by age
age_groups<-group_by(pf,age)
pf.fc_by_age1<-summarise(age_groups,
          friend_count_mean=mean(friend_count),
          friend_count_median=median(as.numeric(friend_count)),
          friend_count_IQR=IQR(friend_count),
          n=n() #number of users in each group
          )
head(pf.fc_by_age1)

##chain functions onto our dataset, perform one function after another
##same as above
pf.fc_by_age2<-pf %>%
  group_by(age) %>%
  summarise(friend_count_mean=mean(friend_count),
          friend_count_median=median(as.numeric(friend_count)),
          n=n()) %>%
  arrange(desc(age))
head(pf.fc_by_age2)

```

## geom line
http://ggplot2.tidyverse.org/reference/geom_path.html
```{r Conditional means plot}
ggplot(data=pf.fc_by_age1,
       aes(age,friend_count_mean))+
  geom_jitter(alpha=0.95,
              aes(size=age,
                  color=age),
              shape=2)

ggplot(data=pf.fc_by_age1,
       aes(age,friend_count_mean))+
  geom_line()

ggplot(data=pf.fc_by_age1,
       aes(age,friend_count_mean))+
  geom_step()
```

