http://rstudio-pubs-static.s3.amazonaws.com/11068_8bc42d6df61341b2bed45e9a9a3bf9f4.html
```{r}
#install.packages('dplyr',dependencies = TRUE)
```
```{r}
library(dplyr)
library(ggplot2)
```
```{r}
pf<-read.delim('pseudo_facebook.tsv')
str(pf)

```
## Basic verbs
dplyr provides five basic data manipulation verbs that work on a single table: filter(), arrange(), select(), mutate() and summarise().

### Filter rows with filter()

+ filter() allows you to select a subset of the rows of a data frame. The first argument is the name of the data frame, and the second and subsequent are filtering expressions evaluated in the context of that data frame
+ filter() works similarly to *subset()* except that you can give it any number of filtering conditions which are joined together with & 
+ This is equivalent to the more verbose: pf[pf$age=='male']
```{r}
pf_f<-filter(pf,gender=='male',age>21,age<23,dob_month==1)
head(pf_f)
```
## Arrange rows with arrange()
+ arrange() works similarly to filter() except that instead of = filtering or selecting rows, it reorders them.   
+ It takes a data frame, and a set of column names (or more complicated expressions) to order by. Use *desc()* to order a order in descending order:  
+ dplyr::arrange() works the same way as plyr::arrange(). It's a straighforward wrapper around order() that requires less typing. The previous code is equivalent to:    
hflights[order(hflights$DayofMonth, hflights$Month, hflights$Year), ]
```{r}
pf_a<-arrange(pf,age,dob_year,desc(tenure))
head(pf_a)
```
## Select columns with select()

+ This function works similarly to the select argument to the base::subset(). It's its own function in dplyr, because the dplyr philosophy is to have small functions that each do one thing well.
+ Often you work with large datasets with many columns where only a few are actually of interest to you. select() allows you to rapidly zoom in on a useful subset using operations that usually only work on numeric variable positions
```{r}
# Select columns by name
s1<-select(pf,age,dob_year)
head(s1)
# Select all columns between Year and DayOfWeek (inclusive)
s2<-select(pf, age:dob_year)
head(s2)
# Select all columns except Year and DayOfWeek
s3<-select(pf, -(age:dob_year))
head(s3)
```
## Add new columns with mutate()

+ As well as selecting from the set of existing columns, it's often useful to add new columns that are functions of existing columns. This is the job of mutate():
+ dplyr::mutate() works the same way as plyr::mutate() and similarly to base::transform(). The key difference between mutate() and transform() is that mutate allows you to refer to columns that you just created:
```{r}
pf_m<-mutate(pf,
       friend_received=friend_count-friendships_initiated,
       tenure_y=tenure/365
       )
head(pf_m,8)

```
## Summarise values with summarise()
The last verb is summarise(), which collapse a data frame to a single row.
```{r}
summarise(pf,
          tenure_med=median(tenure,na.rm = TRUE),
          age_avg=mean(age,na.rm = TRUE)
          )

```

## Commonalities
You may have noticed that all these functions are very similar:

+ The first argument is a data frame.
+ The subsequent arguments describe what to do with it, and you can refer to columns in the data frame directly without using $.
+ The result is a new data frame
Together these properties make it easy to chain together multiple simple steps to achieve a complex result.

# Grouped operations
These verbs are useful, but they become really powerful when you combine them with the idea of ¡°group by¡±, repeating the operation individually on each group. 
+ In dplyr, you use the **group_by()** function to describe how to break a dataset down into groups. You can then use the resulting object in the exactly the same functions as above.
+ Of the five verbs, *arrange() and select()* are unaffected by grouping. 
+ Group-wise *mutate() and arrange()* are most useful in conjunction with window functions, and are described in detail in the corresponding vignette(). 
+ *summarise()* is easy to understand any very useful, and is described in more detail below.
+ You use summarise() with aggregate functions, which take a vector of values, and return a single number. There are many useful functions in base R like *min(), max(), mean(), sum(), sd(), median(), and IQR()*. 
```{r}
#str(pf)
pf_f<-filter(pf,!is.na(gender),!is.na(tenure))
names(pf_f)
##first groupby,second summarise
age_groups<-group_by(pf_f,age)
pf_by_age<-summarise(age_groups,
          count=n(),
          tenure_avg=mean(tenure),
          tenure_IQR=IQR(tenure)
          )

pf_by_age
##same result
by(pf_f$tenure,pf_f$gender,mean)

ggplot(data=pf_by_age,
       aes(x=age,y=tenure_avg))+
  geom_point(aes(size=tenure_avg),alpha=1/5)+
  geom_smooth()
```
```{r}
dob_day_groups<-group_by(pf,dob_year,dob_day,dob_month)
pf_by_dob<-summarise(dob_day_groups,
                     age_avg=mean(age),
                     tenure_avg=mean(tenure))
pf_by_dob
```

