# Connect observations
http://ggplot2.tidyverse.org/reference/geom_path.html
*geom_path()* connects the observations in the order in which they appear in the data.    *geom_line()* connects them in order of the variable on the x axis.   
*geom_step()* creates a stairstep plot, highlighting exactly when changes occur.     
The *group* aesthetic determines which cases are connected together.
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
data("economics")

str(economics)
summary(economics)
```
```{r}
eco<-arrange(economics,date)
date<-eco$date
date[1:3]
length(date)
```

## Example
### geom_line() is suitable for time series
```{r}
p1<-ggplot(data=economics,
           aes(date,unemploy))+
  geom_line(linetype=4)

p2<-ggplot(economics_long,
       aes(x=date,y=value01,
           color=variable))+
  geom_line()
grid.arrange(p1,p2,ncol=1)
```

### geom_step() is useful when you want to highlight exactly when the y value chanes
```{r}
recent<-filter(economics,date>as.Date("2013-01-01"))
p1<-ggplot(recent,
       aes(date,unemploy))+
  geom_line(aes(color=date))

p2<-ggplot(recent,
           aes(date,unemploy))+
  geom_step(aes(color=date))

p3<-ggplot(recent,
           aes(date,unemploy))+
  geom_path(aes(color=date))

grid.arrange(p1,p2,p3,ncol=1)
```
# geom_path lets you explore how two variables are related over time,
# e.g. unemployment and personal savings rate
```{r}
m <- ggplot(economics, aes(unemploy/pop, psavert))
p1<-m + geom_point()
p2<-m + geom_path(aes(color=as.numeric(date)))
grid.arrange(p1,p2,ncol=1)
```
## Changing parameters 
```{r}
?arrow
```

```{r}
p1<-ggplot(economics, aes(date, unemploy)) +
  geom_line(aes(colour = date))
# Use the arrow parameter to add an arrow to the line
# See ?arrow for more details
p2<-ggplot(economics, aes(x = date, y = pop))+
  geom_line(arrow = arrow(angle = 15, 
                          ends = "both", type = "closed"))
grid.arrange(p1,p2,ncol=1)
```
## Control line join parameters
```{r}
#NAs break the line. Use na.rm = T to suppress the warning message
df <- data.frame(x = 1:5, y = c(4,1,NA,9,14))
df
ggplot(df,aes(x,y))+
  geom_path(size=1, linejoin = "mitre",
            lineend='round',linetype=3)+
  geom_point(size=2,aes(color=x))
```

