Lesson 5
========================================================
```{r}
pf<-read.csv("pseudo_facebook.tsv",sep='\t')
library(dplyr)
library(ggplot2)
```


### Third Qualitative Variable--method1
#### Set the color parameter to add the third qualitative variable in the plot.

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) +
  geom_boxplot()+
  stat_summary(fun.y=mean,geom='point',shape=4)
#Everywhere the median friend_count is larger for women than it is for man
#There are some noisy estimates for our old users.
ggplot(data=subset(pf,!is.na(gender)),
       aes(x=age,y=friend_count,color=gender))+
  geom_line(stat='summary',fun.y=median)
  
```
### Third Qualitative Variable--method2
### Plotting Conditional Summaries

```{r Plotting Conditional Summaries}
pf.fc_by_age<-pf %>%
  filter(!is.na(gender)) %>%
  group_by(age,gender) %>%
  summarise(fc_mean=mean(friend_count),
            fc_median=median(as.numeric(friend_count)),
            n=n()) %>%
  arrange(age)

ggplot(data=pf.fc_by_age,
       aes(x=age,y=fc_median))+
  geom_line(aes(color=gender),stat='summary',fun.y=median)+
  geom_smooth()
```
## Third Qualitative Variable--method3
#### facet by third qualitative variable
```{r}
ggplot(data=filter(pf,!is.na(gender)),
       aes(x=age,y=friend_count))+
  facet_grid(.~gender)+
  geom_line(stat='summary',fun.y=median)
  
```
## Third Qualitative Variable--method4
### Wide and Long Format/Reshape data
[convert long data format to a wide format](http://www.cookbook-r.com/Manipulating_data/Converting_data_between_wide_and_long_format/)
[reshape2](http://seananderson.ca/2013/10/19/reshape.html)  
[tidyr](https://s3.amazonaws.com/udacity-hosted-downloads/ud651/DataWranglingWithR.pdf)  
[melt](https://www.r-bloggers.com/melt/)
```{r}
head(pf.fc_by_age)
#install.packages('reshape2')
library(reshape2)
```
```{r}
#long to wide 
#choose the long dataset's key-value pair
pf.fc_by_age_gender.wide<-
  dcast(pf.fc_by_age,
     age~gender,
     value.var = 'fc_median')
head(pf.fc_by_age_gender.wide)

library(gridExtra)
age_male<-ggplot(data=pf.fc_by_age_gender.wide,
       aes(x=age,y=male))+
  geom_line()
age_female<-ggplot(data=pf.fc_by_age_gender.wide,
       aes(x=age,y=female))+
  geom_line()
grid.arrange(age_male,age_female,ncol=2)
```


### Ratio Plot
The gender difference is largest for young users.
How many times more friends does the average female user have than the male user?
```{r Ratio Plot}
ggplot(data=pf.fc_by_age_gender.wide,
       aes(x=age,y=female/male))+
  geom_line()+
  geom_point(alpha=1/5)+
  geom_hline(yintercept = 1,alpha=0.5,linetype=2)+
  geom_vline(xintercept = c(30,60,90),
             alpha=0.5,linetype=4)
?geom_hline
```

