### Third Quantitative Variable

```{r Third Quantitative Variable}
pf$year_joined<-floor(2014-pf$tenure/365)
table(pf$year_joined)

str(pf$year_joined)
```

***

### Cut a Variable
turn numeric variable into factor variable
```{r Cut a Variable}
pf$year_joined.bucket<-cut(pf$year_joined,
                           c(2004,2009,2011,2012,2014))
table(pf$year_joined.bucket,useNA = 'ifany')
str(pf$year_joined.bucket)
```

***

### Plotting it All Together
As the numeric variable turned into factor variable, the method of plot is the same as chapter 1.0 
```{r Plotting it All Together}

ggplot(data=filter(pf,!is.na(year_joined.bucket)),
       aes(x=age,
           y=friend_count))+
  geom_line(aes(color=year_joined.bucket),stat='summary',fun.y=median)
  
```
it indicates that users with higher tenure tend to have higher friend counts, with the exception of our old friends.
***

### Plot the Grand Mean
grand mean line reveals that much of data in the sample is about members of recent cohorts.
```{r Plot the Grand Mean}
ggplot(data=filter(pf,!is.na(year_joined.bucket)),
       aes(x=age,
           y=friend_count))+
  geom_line(aes(color=year_joined.bucket),stat='summary',fun.y=mean)+
  geom_line(stat='summary',fun.y=mean,linetype=4)


```

***

### Friending Rate

```{r Friending Rate}
with(subset(pf,tenure>=1),summary(friend_count/tenure))

ggplot(data=filter(pf,!is.na(pf$gender),tenure>1),
       aes(x=gender,y=friend_count/tenure))+
  geom_boxplot()+
  coord_cartesian(ylim=c(0,4))
```

***

### Friendships Initiated
People with more tenure, typically initiate less friendships.   
friendships_initiated----tenure
```{r Friendships Initiated}
ggplot(data=filter(pf,tenure>=1),
       aes(x=tenure,y=friendships_initiated/tenure))+
  geom_line(aes(color=year_joined.bucket),stat='summary',fun.y=mean)

```

***

### Bias-Variance Tradeoff Revisited
http://scott.fortmann-roe.com/docs/BiasVariance.html

It's noisy, since wr are plotting the mean of y for every possible tenure x value   
We will modify this by bending x axis differently.
```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, 
           y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)
#The code changing the binning is substituting x = tenure in the plotting expressions with x = 7 * round(tenure / 7), etc., binning values by the denominator in the round function and then transforming back to the natural scale with the constant in front.
#tenure n-distinct decrease, so after groupby and summary, the new dataset will have fewer data points.
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```
```{r}
ggplot(aes(x = tenure, 
           y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1))+
  geom_smooth(aes(color=year_joined.bucket))
#R will automatically choose the appropriate statistical methods based on our data.
```

